Exploring the Types and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-11 thesis/paper.tex
More re-strucutring
Results structure

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1}] How do companies actively drive API evolution?
\item[\textbf{RQ1.1}] To what extent can we reverse engineer API change decisions?
\item[\textbf{RQ2}] How do APIs ``passively'' evolve?

@@

%Reasons for choosing case study
The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ1.1}.

@@

%Lehman's - RQ2
The analysis of the trends and the changes, combined with information gathered during the interview, allowed us to answer \textbf{RQ2} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.

%RQ1.1
The final stage of analysis was conducted once all the data had been analysed, which allowed us to answer \textbf{RQ1.1}. This was accomplished by comparing our analysis and interpretation of the change motives against the opinions expressed during the interview. Success was determined by the amount of correct interpretations made about the motives of the changes. Our ability to correctly predict the motives, compared to the designers' actual motives which were made clear during the interviews, served as the basis for answering \textbf{RQ1.1}.

@@

\section{Results} \label{results} 
This section will present the findings of our study. The results related to \textbf{RQ1} and \textbf{RQ1.1} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ2} are presented in Section \ref{results_rq2}

@@

\smallskip \noindent
\textbf{Enhancive  }

\smallskip \noindent
\textbf{Corrective  }

\smallskip \noindent
\textbf{Reductive  }

\smallskip \noindent
\textbf{Adaptive  }

\smallskip \noindent
\textbf{Performance  }

\smallskip \noindent
\textbf{Preventive  }

\smallskip \noindent
\textbf{Groomative  }

\smallskip \noindent
\textbf{Updative  }

\smallskip \noindent
\textbf{Reformative  }

\smallskip \noindent
\textbf{Evaluative  }

\smallskip \noindent
\textbf{Consultive  }

\smallskip \noindent
\textbf{Training  }

@@

\subsection{Reverse Results}

@@

\subsection{RQ2 Results} \label{results_rq2} 
\noindent
RQ2: \textbf{How do APIs ``passively'' evolve?}
\smallskip

The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.

@@

@@

\subsection{Discussion RQ1.1}

@@

@@

% \noindent
% RQ1.1: \textbf{To what extent can we reverse engineer API change decisions?}
% \smallskip

>>>>

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1}] How do companies actively drive API evolution?
\item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?
\item[\textbf{RQ3}] How do APIs ``passively'' evolve?

@@

%Reasons for choosing case study
The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ2}.

@@

%Lehman's - RQ3
The analysis of the trends and the changes, combined with information gathered during the interview, allowed us to answer \textbf{RQ3} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.

%RQ2
The final stage of analysis was conducted once all the data had been analysed, which allowed us to answer \textbf{RQ2}. This was accomplished by comparing our analysis and interpretation of the change motives against the opinions expressed during the interview. Success was determined by the amount of correct interpretations made about the motives of the changes. Our ability to correctly predict the motives, compared to the designers' actual motives which were made clear during the interviews, served as the basis for answering \textbf{RQ2}.

@@

\newpage

\section{Results} \label{results} 
This section will present the findings of our study. The results related to \textbf{RQ1} and \textbf{RQ2} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ3} are presented in Section \ref{results_RQ3}

@@

\smallskip \noindent
\textbf{Enhancive  }
We have found enhancive changes to be a large part of the API's evolution. Examples are...

\smallskip \noindent
\textbf{Corrective  }
Corrective changes have been a driving force for the evolution of the API...

\smallskip \noindent
\textbf{Reductive  }
Only one reductive change was found...

\smallskip \noindent
\textbf{Adaptive  }
No adaptive changes were found

\smallskip \noindent
\textbf{Performance  }
No identified changes could be related to performance...

\smallskip \noindent
\textbf{Preventive  }
Preventive changes were...

\smallskip \noindent
\textbf{Groomative  }
A couple of groomative changes were found...

\smallskip \noindent
\textbf{Updative  }
Updative changes only affected documentation and not code...

\smallskip \noindent
\textbf{Reformative  }
Blabla...

\smallskip \noindent
\textbf{Evaluative  }
Blabla...

\smallskip \noindent
\textbf{Consultive  }
Blabla...

\smallskip \noindent
\textbf{Training  }
Blabla...

@@

\newpage
\subsection{RQ2 Results}

@@

\newpage

\subsection{RQ3 Results} \label{results_RQ3} 
\noindent
RQ3: \textbf{How do APIs ``passively'' evolve?}
\smallskip

The results related to \textbf{RQ3} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.

@@

\subsubsection{Lehman's Laws}

@@

@@

\newpage

\subsection{Discussion RQ3}

@@

% \noindent
% RQ2: \textbf{To what extent can we reverse engineer API change decisions?}
% \smallskip
